data_collation

### 2024-06-20 scripts/data_cleaning.Rmd
made temp analysis and table
updated rugosity models

# Rename Kings Beach to King's Beach
rug_data$SITE[rug_data$SITE == "Kings Beach"] <- "King's Beach"
rug_data$SITE[rug_data$SITE == "KB"] <- "King's Beach"
rug_data$SITE[rug_data$SITE == "Fort Weatherill"] <- "Fort Wetherill"
rug_data$SITE[rug_data$SITE == "Ft. Weatherill"] <- "Fort Wetherill"
rug_data$TRANSECT[rug_data$TRANSECT == "Control 1"] <- "1"
rug_data$TRANSECT[rug_data$TRANSECT == "Control 2"] <- "2"

>>>>

# Rename Kings Beach to King's Beach
rug_data$SITE[rug_data$SITE == "Kings Beach"] <- "King's Beach"
rug_data$SITE[rug_data$SITE == "KB"] <- "King's Beach"
rug_data$SITE[rug_data$SITE == "Fort Weatherill"] <- "Fort Wetherill"
rug_data$SITE[rug_data$SITE == "Ft. Weatherill"] <- "Fort Wetherill"
rug_data$TRANSECT[rug_data$TRANSECT == "Control 1"] <- "5"
rug_data$TRANSECT[rug_data$TRANSECT == "Control 2"] <- "6"
